### 2023-04-19 paper.Rmd
update table numbers

Table 1 displays the global simulation results aggregated across all conditions. Standard k-means performed best at minimizing discrepancy with regard to means ($\Delta \mathit{M}$), but did not outperform a random assignment with regard to all other distribution characteristics. Replicating @papenberg2020, k-means' performance with regard to similarity in standard deviations was even below that of a random assignment. K-plus anticlustering addressed $\Delta \mathit{M}$ almost as well as k-means, and at the same time minimized discrepancy with regard to the standard deviations ($\Delta \mathit{SD}$); both k-plus approaches strongly outperformed all other methods with regard to minimizing $\Delta \mathit{SD}$.

@@

This section demonstrates how readers can easily employ k-plus anticlustering using the R package `anticlust` [@papenberg2020] using the function `kplus_anticlustering()`, which is available from version 0.6.3 onward. The package can be installed in the R environment using the `install.packages()` command:

@@

Table 2 shows the results of the anticlustering application by listing the descriptive statistics (means, standard deviations and skewness) for each of the 9 groups and for each of the 3 features. Table 2 also contains the results after applying k-means anticlustering and diversity anticlustering. It is shown that---up to two decimals---k-plus anticlustering perfectly matched all groups with regard to the features' means and standard deviations, and the skewness was also very evenly matched. K-means anticlustering also perfectly matched the mean values, but showed decreased performance with regard to similarity in standard deviations and skewness. Diversity anticlustering was well-suited to match means, standard deviations and skew, but was slightly outperformed by k-plus. The latter result is not surprising because---unlike k-plus anticlustering---diversity anticlustering does not directly maximize similarity with regard to these criteria, but instead maximizes within-group heterogeneity.

@@

Table 3 illustrates another advantage of k-plus anticlustering over diversity anticlustering: When creating groups of unequal size, diversity anticlustering tends to increase the spread of the data in the largest group in comparison to the other groups. K-plus anticlustering strives for between-group similarity regardless of group size. Unequal group sizes can be requested by passing the different group sizes to the argument `K`. The following code was used to equalize means and variances between four groups using the k-plus approach:

@@

Table 4 illustrates the results that are obtained when using standard[^standardkplus] k-plus anticlustering to divide the stimulus set into 6 groups of size `r nrow(schaper2019) / 6` each. Even though the means and standard deviations are no longer perfectly matched between groups, arguably they are similar enough for any practical purposes.

>>>>

Table 2 displays the global simulation results aggregated across all conditions. Standard k-means performed best at minimizing discrepancy with regard to means ($\Delta \mathit{M}$), but did not outperform a random assignment with regard to all other distribution characteristics. Replicating @papenberg2020, k-means' performance with regard to similarity in standard deviations was even below that of a random assignment. K-plus anticlustering addressed $\Delta \mathit{M}$ almost as well as k-means, and at the same time minimized discrepancy with regard to the standard deviations ($\Delta \mathit{SD}$); both k-plus approaches strongly outperformed all other methods with regard to minimizing $\Delta \mathit{SD}$.

@@

This section demonstrates how readers can easily employ k-plus anticlustering using the R package `anticlust` [@papenberg2020] using the function `kplus_anticlustering()`, which implements the unweighted sum approach for k-plus anticlustering. The package can be installed in the R environment using the `install.packages()` command:

@@

Table 3 shows the results of the anticlustering application by listing the descriptive statistics (means, standard deviations and skewness) for each of the 9 groups and for each of the 3 features. Table 3 also contains the results after applying k-means anticlustering and diversity anticlustering. It is shown that---up to two decimals---k-plus anticlustering perfectly matched all groups with regard to the features' means and standard deviations, and the skewness was also very evenly matched. K-means anticlustering also perfectly matched the mean values, but showed decreased performance with regard to similarity in standard deviations and skewness. Diversity anticlustering was well-suited to match means, standard deviations and skew, but was slightly outperformed by k-plus. The latter result is not surprising because---unlike k-plus anticlustering---diversity anticlustering does not directly maximize similarity with regard to these criteria, but instead maximizes within-group heterogeneity.

@@

Table 4 illustrates another advantage of k-plus anticlustering over diversity anticlustering: When creating groups of unequal size, diversity anticlustering tends to increase the spread of the data in the largest group in comparison to the other groups. K-plus anticlustering strives for between-group similarity regardless of group size. Unequal group sizes can be requested by passing the different group sizes to the argument `K`. The following code was used to equalize means and variances between four groups using the k-plus approach:

@@

Table 5 illustrates the results that are obtained when using standard[^standardkplus] k-plus anticlustering to divide the stimulus set into 6 groups of size `r nrow(schaper2019) / 6` each. Even though the means and standard deviations are no longer perfectly matched between groups, arguably they are similar enough for any practical purposes.
